\chapter{Introduction}
\label{ch:introduction}

In 1998, accessing the Internet required a clunky desktop computer and a dial-up
subscription. When Apple integrated WiFi into its iBook computers under the
brand name “AirPort” the following year, it forced other industry giants to
compete and revolutionized wireless networking ~\cite{_brief_2004}. If not for
the adoption of this technology along with the advent of wireless data-enabled
and commercially available cell phones such as Nokia’s Communicator 9000
~\cite{_first_1996}, cell phones would never have evolved to surpass their
primary function as telephones and become the communication necessity they are
today.

The ubiquity of WiFi and wireless communication revolutionized the way society
interacts with the Internet. Suddenly, portable devices became powerful
standalone devices rather than accessories to their desk-bound counterparts.
Cell phones rivaled computers in necessity and ubiquity, and eclipsed their
predecessors in terms of productivity. Coffee shops, airports, and hotels
transformed from physical meeting places to universal hotspots, enabling the
masses to bridge distances, connect instantly, and effectively trivialize time
and space quite literally in the palms of their hands. This is the power of
wireless technology.

So then, why does society continue to labor under the burden of wires? Having
enjoyed rewards of another relatively nascent wireless technology, why do we
hesitate to cut the cord?

Wireless power transfer (WPT)-enabled mobile devices have the potential to be a
disruptive technology on the consumer technology market.  Investments in WPT
have grown dramatically in the past decade, and more technologies have started
integrating WPT into their systems at the consumer level.

The result is a growing number of WPT methods seeing practical application.
These techniques can successfully power and charge a wide range of consumer
products, from cell phones to cars.  However, they still face significant
disadvantages in transmission distance and efficiency.  Most require line of
sight to operate.

Gemstone Team TESLA proposes time-reversed electromagnetic wave propagation (to
be abbreviated "time-reversal" or "TR" in this document) as a novel WPT method.
In particular, TR’s ability to maintain connection even when line of sight is
lost opens up a new range of possible applications.  To support this proposal,
the team has performed a number of exploratory experiments on the topic of TR
applied to WPT.  These experiments are concerned primarily with understanding
the fundamental engineering realities that would be necessary to build a working
TR WPT system.

In this paper, TESLA overviews the state of the art of both consumer wireless
power transfer technologies and time reversal.  Major innovations are outlined,
as are current limitations.  The team’s experiments are then detailed
individually.  The purpose, methodology, and results for each experiment are
explained.  The results of each experiment and their significance are then
discussed in the context of TR WPT.  The results of the team as a whole are
discussed in a similar way.  Finally, the team makes suggestions for future
research that could be made in this field, for the benefit of future
researchers.
